---
title: "Transparent Backgrounds for Plot"
description: |
  Remove background of plots
author:
  - name: Emil Hvitfeldt
    url: {}
date: 05-22-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - plot
preview: preview.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

If you are using a non-white background color for your slides it can be bothersome to match the background of your plots. Setting `dev.args = list(bg = 'transparent')` in your chunk option removes the background of your chart and it will show the background color of the slide instead.

Note, you most likely have to change the text colors of your chart to be move visible under the new background.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/examples/transparent-plot/index.html", 
  ratio = "4:3"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../static/examples/transparent-plot/index.Rmd"), sep = "\n")
```
