---
title: "Chaining Content Classes"
description: |
  Syntax trick for cleaner use of content classes
author:
  - name: Emil Hvitfeldt
    url: {}
date: 05-20-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - css
  - content classes
preview: preview.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Content classes are a great tool when creating xaringan slides. Chaining is a way to apply multiple content classes to the same element with a more concise syntax.

If you were to apply `.italic` and `.orange` to a word you could write it as
`.italic[.orange[word]]` which is already bad with just 2 classes. Chaining allows us to write `.italic.orange[word]` to get the same result.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/examples/chaining-content-classes/index.html", 
  ratio = "4:3"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../static/examples/chaining-content-classes/index.Rmd"), sep = "\n")
```

# stylesheet.css

```{r, echo=FALSE, class.output = "cssfile"}
cat(readr::read_lines("../../static/examples/chaining-content-classes/stylesheet.css"), sep = "\n")
```
