---
title: "lexis theme"
description: |
  Themes by John Paul Helveston
author:
  - name: John Paul Helveston
date: 06-04-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - theme
preview: preview.gif
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


λέξις (lexis) is a theme for the [xaringan Rpackage](https://github.com/yihui/xaringan) for making slides. It has a light gray background and uses [Fira Sans Condensed](https://fonts.google.com/specimen/Fira+Sans+Condensed) for headers, [Inter](https://fonts.google.com/specimen/Inter) for body text, and [SFMono-Regular](https://developer.apple.com/fonts/) for mono text (i.e. code). The theme copies ideas from several other themes, most notably from [Allison Hill](https://alison.rbind.io/)'s xaringan [workshop](https://github.com/rstudio-education/arm-workshop-rsc2019). It also uses many of the wonderful features from [Garrick Aden-Buie](https://garrickadenbuie.com/)'s [xaringanExtra](https://pkg.garrickadenbuie.com/xaringanExtra/#/) package.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/themes/lexis-theme/index.html", 
  ratio = "16:9"
)
```

# Material

All material can be found [here](https://github.com/jhelvy/lexis).
