---
title: "Adjustable Pull"
description: |
  Adjust the widths of .pull-left and .pull-right
author:
  - name: Emil Hvitfeldt
    url: {}
date: 05-20-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - css
  - content classes
  - pull
preview: preview.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Content classes such as `.pull-left` and `.pull-right` are very useful to organize material in your slides. They come with a default width that you would change, but it isn't really worth it to do it globally in your slides.

With the use of changed content classes, you can specify the width of `.pull-left` and `.pull-right` on a case-by-case basis. The `"widths.css"` file contains content classes for different widths using the names `w*` where `*` is a percentage. Typing `.pull-left.w40` would create a column on the left with a width of `40%`. The order doesn't matter so ``.w40.pull-left` would work as well.

Note that `"widths.css"` must be placed after `"default"` in `xaringan::moon_reader: css`.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/examples/adjustable-pull/index.html", 
  ratio = "4:3"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../static/examples/adjustable-pull/index.Rmd"), sep = "\n")
```

# width.css

```{r, echo=FALSE, class.output = "cssfile"}
cat(readr::read_lines("../../static/examples/adjustable-pull/widths.css"), sep = "\n")
```
