---
title: "NES xaringan theme <i class='nes-icon coin'></i>"
subtitle: "Inspired by NES.css"
author: "Emil Hvitfeldt"
output:
  xaringan::moon_reader:
    css: ["style.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Header 1

## Header 2

### Header 3

Normal text

**Bold text**

*italics*

~~strikethrough~~

[links](https://www.xaringan.gallery/).

---

# Code expressions

Code chunks and output

```{r}
lm(mpg ~ disp, data = mtcars)
```

---

# Block quotes

> Dorothy followed her through many of the beautiful rooms in her castle.

---

# Ordered list

1. First item
2. Second item
3. Third item
    1. Indented item
    2. Indented item
4. Fourth item

---

# Unordered list

- First item
- Second item
- Third item
- Fourth item

---

# ggplot2

```{r scatter, fig.show='hide', warning=FALSE}
library(ggplot2)
library(palmerpenguins)

colors <- c("#76c442", "#f2c409", "#ce372b")

ggplot(penguins) +
  aes(bill_length_mm, bill_depth_mm,
      color = species) +
  geom_point() +
  theme_minimal(base_family = "Press Start 2P") +
  scale_color_manual(values = colors) -> ppp
```

Must have installed [Press Start 2P](https://fonts.google.com/specimen/Press+Start+2P) font

---

class: center

# ggplot2

```{r, echo=FALSE, fig.asp=0.618, warning=FALSE, dev='svg'}
ppp
```

---

class: center

# Thank you!

<i class="nes-icon twitter"></i> @Emil_Hvitfeldt

<i class="nes-icon github"></i> EmilHvitfeldt

<i class="nes-icon linkedin"></i> EmilHvitfeldt
