---
title: "Side by Side Code and Plot"
description: |
  Show code and plot on same slide without copy-paste
author:
  - name: Emil Hvitfeldt
    url: {}
date: 05-22-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - plot
  - pull
preview: preview.gif
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

If you want to show your code AND plots you can use the `.pull-left[]` and `.pull-right[]` content classes. To avoid copy-paste of the code you can use some `knitr` magic to have the code shown in one place and have the results rendered another place.

### Code first

When you are doing code first you set the following options in the code chunk `chunkname, fig.show="hide"` and put

```{r, eval=FALSE}
knitr::include_graphics(
  knitr::fig_chunk("chunkname", "png")
)
```

where you want the figure to appear. The `chunkname` must match.

### Plot first

The previous approach does not work if you want the plot to appear before the text. To make this work you need to set the following chunk options

- plot chunk: `ref.label="chunkname", echo=FALSE`
- code chunk: `chunkname, fig.show='hide'`

Note, if you want to do this multiple times in a slide deck you need to specify a different `chunkname` for each pair of chunks.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/examples/side-by-side-code-plot/index.html", 
  ratio = "16:9"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../static/examples/side-by-side-code-plot/index.Rmd"), sep = "\n")
```
