---
title: "typed"
description: |
  A short description of the post.
author:
  - name: Emil Hvitfeldt Hansen
date: 05-11-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - typed.js
preview: preview.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Animated self-typing can be a fun addition to your slides.

These examples use the [Typed.js](https://github.com/mattboldt/typed.js/) javascript library to animate the text. The repository includes a handful of good examples and [a list of parameters](https://github.com/mattboldt/typed.js/#customization).

Notes:

I found that you must use all the typed objects you create for them to work in xaringan. E.i. If you want to used `.typed2[]` you must have called `.typed[]` as well. Furthermore, you can only use each typed object once.

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../typed/index.html", 
  ratio = "4:3"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../typed/index.Rmd"), sep = "\n")
```

# typed.js

```{r, echo=FALSE, class.output = "css"}
cat(readr::read_lines("../../typed/typed.js"), sep = "\n")
```
