---
title: "Hex Header"
description: |
  Add row of hexes to header of slide
author:
  - name: Emil Hvitfeldt
    url: {}
date: 05-22-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - css
preview: preview.png
---

A row of hex stickers at the top of a slide is a great way to indicate to the viewer what packages are being used when.

We can accomplish this using a custom function `hexes` and a css class.

Simply put the required hex stickers in the `images/` folder. (code assumes that all hexes are .png files) and add this to the end of a header to include the hexes.

```{r, eval=FALSE}
`r hexes("xaringan")`
```

Trick by [Max Kuhn](https://twitter.com/topepos)

# Result

```{r, echo=FALSE}
xaringanExtra::embed_xaringan(
  url = "../../static/examples/hex-header/index.html", 
  ratio = "4:3"
)
```

# Rmd

```{r, echo=FALSE, class.output = "rmd"}
cat(readr::read_lines("../../static/examples/hex-header/index.Rmd"), sep = "\n")
```

# style.css

```{r, echo=FALSE, class.output = "css"}
cat(readr::read_lines("../../static/examples/hex-header/style.css"), sep = "\n")
```
